---
title: "Merge_all_CCA"
output: html_document
date: "2022-11-27"
---
---
---

# Split Data into Saline and Cocain samples

## Load Saline samples

```{r}
require(Seurat)
require(stringr)
options(future.globals.maxSize = 2000 *1024^2)
source("utils.R")
Saline_cellRangerPaths <- list(
  PFCSample2 = "../../PFC_sample2/",
  PFCSample3 = "../../PFC_sample3/",
  PFCSample5 = "../../PFC_sample5/",
  PFCSample7 = "../../PFC_sample7/",
  PFCSample11 = "../../PFC_sample11/",
  PFCSample12 = "../../PFC_sample12/"
  )
```

### Create Seurate objects 


```{r}
Saline_sobjPerSample <- list()
samples <- c('PFCSample2', 'PFCSample3','PFCSample5',
             'PFCSample7','PFCSample11','PFCSample12')       
for (sample in samples) {                  #start a For loop
  scrna_data <- Read10X(                   #read 10X dataset 3 tables
    data.dir = str_c("C:/Users/Eric Teng/OneDrive/Desktop/R/My Project/", sample)) #specify file path
  seob <- CreateSeuratObject(              #create Seurat objects
    counts = scrna_data,
    project = sample)                    
  seob[['sample']] <- sample               
 Saline_sobjPerSample[[sample]] = seob 
 Saline_sobjPerSample[[sample]] = RenameCells(Saline_sobjPerSample[[sample]],add.cell.id = sample)
Saline_sobjPerSample[[sample]]@meta.data$Sample = sample    
}
```

### Merge objects

```{r}
PFCmerged_saline_sobj <- NULL




for(i in 1:(length(names(Saline_sobjPerSample))-1)){
  j=i+1
  message(paste("Merging with",names(Saline_sobjPerSample)[j]))
  if(i==1){

    PFCmerged_saline_sobj <- merge(x = Saline_sobjPerSample[[1]], 
                y = Saline_sobjPerSample[-1], )
  }else{

    normalize <- ifelse(j==length(names(Saline_sobjPerSample)),TRUE,FALSE)
    PFCmerged_saline_sobj <- merge(x = Saline_sobjPerSample[[1]], 
                y = Saline_sobjPerSample[-1],
                                   scale.factor = 1e6,
                                   do.scale = F,
                                   do.center = F,
                                   do.normalize = normalize)
  }

  }
  print(table(str_match(rownames(PFCmerged_saline_sobj@meta.data),pattern = "(\\w+)_(\\w+)")[,2]))


PFCmerged_saline_sobj

# Merging with PFCSample3
# 
# PFCSample2 PFCSample3 
#       1462       1171 
# Merging with PFCSample5
# 
# PFCSample2 PFCSample3 PFCSample5 
#       1462       1171       1705 
# Merging with PFCSample7
# 
# PFCSample2 PFCSample3 PFCSample5 PFCSample7 
#       1462       1171       1705       1887 
# Merging with PFCSample11
# 
# PFCSample11  PFCSample2  PFCSample3  PFCSample5  PFCSample7 
#        4747        1462        1171        1705        1887 
# Merging with PFCSample12
# Performing log-normalization
# 0%   10   20   30   40   50   60   70   80   90   100%
# [----|----|----|----|----|----|----|----|----|----|
# **************************************************|
# 
# PFCSample11 PFCSample12  PFCSample2  PFCSample3  PFCSample5  PFCSample7 
#        4747        3806        1462        1171        1705        1887 
# An object of class seurat in project PFCSample2 
#  26145 genes across 14778 samples.
```


### Normalize data and detect variable genes

```{r}
PFCmerged_saline_sobj <- SetSamplesLabels_PFC(PFCmerged_saline_sobj)
PFCmerged_saline_sobj[["percent.mito"]] <- 
PercentageFeatureSet(PFCmerged_saline_sobj, pattern= '^mt-')
PFCmerged_saline_sobj@meta.data[["percent.mito"]]


PFCmerged_saline_sobj <- NormalizeData(PFCmerged_saline_sobj,scale.factor = 1e6,display.progress = T)
PFCmerged_saline_sobj@meta.data$stage <- paste0(PFCmerged_saline_sobj@meta.data$Period,"_",PFCmerged_saline_sobj@meta.data$treatment)

PFCmerged_saline_sobj <- ScaleData(PFCmerged_saline_sobj,vars.to.regress = c("nCount_RNA","percent.mito"),do.scale = T,do.center = T)



PFCmerged_saline_sobj <- FindVariableFeatures(PFCmerged_saline_sobj,selection.method = "vst", nfeatures = 2000)
length(PFCmerged_saline_sobj@assays[["RNA"]]@var.genes) #758 genes
save(PFCmerged_saline_sobj,file = "PFCmerged_saline_sobj.rdata")

```


## Load Cocaine samples


```{r}
Cocaine_cellRangerPaths <- list(
  PFCSample1 = "../../PFC_sample1/",
  PFCSample4 = "../../PFC_sample4/",
  PFCSample6 = "../../PFC_sample6/",
  PFCSample8 = "../../PFC_sample8/",
  PFCSample9 = "../../PFC_sample9/",
  PFCSample10 = "../../PFC_sample10/"
  )
```

## Create Seurate objects for cocaine

```{r}
Cocaine_sobjPerSample <- list()
samples <- c('PFCSample1', 'PFCSample4','PFCSample6',
             'PFCSample8','PFCSample9','PFCSample10')       
for (sample in samples) {                  #start a For loop
  scrna_data <- Read10X(                   #read 10X dataset 3 tables
    data.dir = str_c("C:/Users/Eric Teng/OneDrive/Desktop/R/My Project/", sample)) #specify file path
  seob <- CreateSeuratObject(              #create Seurat objects
    counts = scrna_data,
    project = sample)                    
  seob[['sample']] <- sample               
 Cocaine_sobjPerSample[[sample]] = seob 
 Cocaine_sobjPerSample[[sample]] = RenameCells(Cocaine_sobjPerSample[[sample]],add.cell.id = sample)
Cocaine_sobjPerSample[[sample]]@meta.data$Sample = sample    
}
```

## merge cocaine

```{r}
PFCmerged_cocaine_sobj <- NULL




for(i in 1:(length(names(Cocaine_sobjPerSample))-1)){
  j=i+1
  message(paste("Merging with",names(Cocaine_sobjPerSample)[j]))
  if(i==1){

    PFCmerged_cocaine_sobj <- merge(x = Cocaine_sobjPerSample[[1]], 
                y = Cocaine_sobjPerSample[-1], )
  }else{

    normalize <- ifelse(j==length(names(Cocaine_sobjPerSample)),TRUE,FALSE)
    PFCmerged_cocaine_sobj <- merge(x = Cocaine_sobjPerSample[[1]], 
                y = Cocaine_sobjPerSample[-1],
                                   scale.factor = 1e6,
                                   do.scale = F,
                                   do.center = F,
                                   do.normalize = normalize)
  }

  }
  print(table(str_match(rownames(PFCmerged_cocaine_sobj@meta.data),pattern = "(\\w+)_(\\w+)")[,2]))


PFCmerged_cocaine_sobj
```

#Normalize
```{r}

PFCmerged_saline_sobj <- NULL

PFCmerged_cocaine_sobj <- SetSamplesLabels_PFC(PFCmerged_cocaine_sobj)

PFCmerged_cocaine_sobj[["percent.mito"]] <- 
PercentageFeatureSet(PFCmerged_cocaine_sobj, pattern= '^mt-')
PFCmerged_cocaine_sobj@meta.data[["percent.mito"]]

PFCmerged_cocaine_sobj <- NormalizeData(PFCmerged_cocaine_sobj,scale.factor = 1e6,display.progress = T)
PFCmerged_cocaine_sobj@meta.data$stage <- paste0(PFCmerged_cocaine_sobj@meta.data$Period,"_",PFCmerged_cocaine_sobj@meta.data$treatment)

PFCmerged_cocaine_sobj <- ScaleData(PFCmerged_cocaine_sobj,vars.to.regress = c("nCount_RNA","percent.mito"),do.scale = T,do.center = T)


PFCmerged_cocaine_sobj <- FindVariableFeatures(PFCmerged_cocaine_sobj,selection.method = "vst", nfeatures = 2000)
length(PFCmerged_cocaine_sobj@assays[["RNA"]]@var.genes) #758 genes
save(PFCmerged_cocaine_sobj,file = "PFCmerged_Cocaine_sobj.rdata")

```


## Do CCA analysis

```{r}

PFC_CCA_cocaine_Saline_sobj <- RunCCA(PFCmerged_saline_sobj, PFCmerged_cocaine_sobj,
                                      features = union(PFCmerged_saline_sobj@assays[["RNA"]]@var.features, PFCmerged_cocaine_sobj@assays[["RNA"]]@var.features))
tmp = PFC_CCA_cocaine_Saline_sobj@meta.data[,c("Sample","nCount_RNA","nFeature_RNA")]
tmp$Sample= as.character(tmp$Sample)
tmp$Sample = gsub("PFC","",tmp$Sample)
tmp$Sample= factor(tmp$Sample,levels = paste0("Sample",12:1))
install.packages("RColorBrewer")
library(RColorBrewer)
library(tidyverse)
cols = rev(brewer.pal(12,"Paired"))
p1= ggplot(tmp, aes(x=Sample, y= nCount_RNA,fill=Sample)) + geom_boxplot(width=0.5) + scale_fill_manual(values = cols) + theme_bw() + coord_flip()
p2= ggplot(tmp, aes(x=Sample, y= nFeature_RNA,fill=Sample)) + geom_boxplot(width=0.5) + scale_fill_manual(values = cols) + theme_bw() + coord_flip()
gridExtra::grid.arrange(p1,p2,nrow=1)
```


```{r}
DimHeatmap(PFC_CCA_cocaine_Saline_sobj,dims = 1:10,reduction = "cca", balanced = TRUE)      
```

#Split objects
```{r}

seob_list <- SplitObject(PFC_CCA_cocaine_Saline_sobj, split.by = "sample")

#finding anchors
features <- SelectIntegrationFeatures(object.list = seob_list,
                                      nfeatures = 2000)

anchors <- FindIntegrationAnchors(object.list = seob_list,
                                  reference = 1,
                                  anchor.features = features
) 
save(PFC_CCA_cocaine_Saline_sobj, file =
       "PFC_CCA_cocaine_Saline_sobj.rdata")

#Datasets integration
PFC_CCA_cocaine_Saline_sobj <- IntegrateData(anchorset = anchors) 

DefaultAssay(PFC_CCA_cocaine_Saline_sobj) <- "integrated"

#Saving object
save(PFC_CCA_cocaine_Saline_sobj, file = "PFC_CCA_cocaine_Saline_sobj_intg.rdata")
```

#Dimension reduc
```{r}

DefaultAssay(PFC_CCA_cocaine_Saline_sobj) <- "integrated"
PFC_CCA_cocaine_Saline_sobj <- ScaleData(PFC_CCA_cocaine_Saline_sobj, verbose = FALSE)
save(PFC_CCA_cocaine_Saline_sobj,file = "PFC_CCA_cocaine_Saline_sobj_scal.rdata")

PFC_CCA_cocaine_Saline_sobj <- RunPCA(PFC_CCA_cocaine_Saline_sobj, npcs = 50, verbose = FALSE)
ElbowPlot(PFC_CCA_cocaine_Saline_sobj, ndims = 50)
PFC_CCA_cocaine_Saline_sobj <- RunUMAP(PFC_CCA_cocaine_Saline_sobj, reduction = "pca", dims = 1:30)
PFC_CCA_cocaine_Saline_sobj <- RunTSNE(PFC_CCA_cocaine_Saline_sobj,
                                       reduction.use = "cca.aligned",dims.use = 1:12)
p1 <- DimPlot(PFC_CCA_cocaine_Saline_sobj, reduction = "tsne", group.by = "sample")
p2 <- DimPlot(PFC_CCA_cocaine_Saline_sobj, reduction = "umap", group.by = "sample")

p1+p2

```

#Clustering
```{r}
PFC_CCA_cocaine_Saline_sobj <- FindNeighbors(PFC_CCA_cocaine_Saline_sobj, reduction = "pca", dims = 1:50)
PFC_CCA_cocaine_Saline_sobj<- FindClusters(PFC_CCA_cocaine_Saline_sobj, resolution = 1.6)

p3 <- DimPlot(PFC_CCA_cocaine_Saline_sobj,
               reduction = "umap",
               group.by  = "seurat_clusters",
               label = T)
p3
p4 <- DimPlot(PFC_CCA_cocaine_Saline_sobj,
               reduction = "tsne",

               group.by  = "seurat_clusters",
               label = T)
p4
```

#dot plot for some markers
```{r}
library(tidyverse)
library(patchwork)
library(Seurat)
BiocManager::install("SummarizedExperiment")
library(SummarizedExperiment)

markers<- c("Snap25","Slc17a7","Gad2", "Flt1","Aspa",
                                          "Gja1",
                                          "Neu4",
                                          "Pdgfra",
                                          "C1qa",
                                          "Cldn5",
                                          "Cd24a",
                                          "Pou3f1","Syt6","Tshz2", "Bmp4", "Mlc1","Neurod6", "Nrn1")
p5 <- DotPlot(object=PFC_CCA_cocaine_Saline_sobj, features = markers) +
     theme(axis.text = element_text(size = 8,
     angle = 90,
     hjust = 1))
p5
```

#verification by different markers

```{r}

markers_2<- c("Mlc1","Gjb6","Aqp4", "Acsbg1","Flt1",
                                          "Cldn5",
                                          "Tm4sf1",
                                          "Pglyrp1",
                                          "Rgs5","Neurod6",
                                          "Slc17a7",
                                          "Nrn1",
                                          "Gad1","Gad2","Pnoc", "Slc32a1",
                                          "C1qa","C1qb",  "C1qc","Ctss","Neu4","Bmp4","Pak4","Enpp6","Brca1","Ermn",
                                          "Opalin","Mog","Aspa","Mobp",
                                          "Pdgfra","Cacng4","Tmem100",
                                          "Matn4","Ptprz1")
p6 <- DotPlot(object=PFC_CCA_cocaine_Saline_sobj, features = markers_2) +
     theme(axis.text = element_text(size = 8,
     angle = 90,
     hjust = 1))
p6
Idents(object = PFC_CCA_cocaine_Saline_sobj) <- "treatment"
PFC_CCA_Saline_sobj <- subset(x = PFC_CCA_cocaine_Saline_sobj, idents = c("Saline"))
PFC_CCA_Cocaine_sobj <- subset(x = PFC_CCA_cocaine_Saline_sobj, idents = c("Cocaine"))
p17 <- FeaturePlot(PFC_CCA_Cocaine_sobj,c("Fosb","rna_Mecp2","Bdnf","Arc", "Egr2","Fos","Jun", "Junb"))
p17
p18 <- FeaturePlot(PFC_CCA_cocaine_Saline_sobj,c("Fosb","rna_Mecp2","Bdnf","Arc", "Egr2","Fos","Jun", "Junb"))
p18

```
## Plot some markers

```{r}
cluster2type <- c(
"0"="Excitatory","1"="Excitatory","2"="Excitatory","3"="Excitatory","4"="Astro","5"="Micro","6"="Excitatory","7"="Excitatory","8"="Endo","9"="Endo",
"10"="Oligo", "11"="Excitatory", "12"="Excitatory","13"="Excitatory",
"14"="Excitatory","15"="Excitatory","16"="Excitatory","17"="Endo","18"="OPC","19"="Excitatory","20"="DD","21"="Astro","22"="Inhibitory","23"="Excitatory","24"="DD","25"="Inhibitory","26"="DD","27"="Oligo","28"="Excitatory","29"="Oligo","30"="NF Oligo","31"="Endo","32"="Inhibitory","33"="DD","34"="DD","35"="DD","36"="DD","37"="Astro","38"="DD","39"="Endo","40"="Astro","41"="Micro","42"="Endo","43"="Oligo","44"="Endo","45"="Micro","46"="OPC","47"="OPC","48"="OPC","49"="OPC","50"="Excitatory","51"="Micro","52"="Excitatory","53"="Excitatory","54"="OPC","55"="Micro","56"="Micro","57"="Astro","58"="DD")

PFC_CCA_cocaine_Saline_sobj[['cell_type']] = unname(cluster2type[PFC_CCA_cocaine_Saline_sobj@meta.data$seurat_clusters])

Idents(object = PFC_CCA_cocaine_Saline_sobj) <- "cell_type" 
PFC_CCA_cocaine_Saline_sobj <- subset(x = PFC_CCA_cocaine_Saline_sobj, idents = c("DD"), invert = TRUE)

p7 <- DimPlot(PFC_CCA_cocaine_Saline_sobj, 
               reduction = "umap", 
               group.by  = "cell_type",
               label = T)
p7
p8 <- DimPlot(PFC_CCA_cocaine_Saline_sobj, 
               reduction = "tsne", 
               group.by  = "cell_type",
               label = T)
p8


```



save(PFC_CCA_cocaine_Saline_sobj, file = PFC_CCA_cocaine_Saline_sobj_cluster.rdata")
```{r fig.height=8, fig.width=12}



FeaturePlot(PFC_CCA_cocaine_Saline_sobj,c("Snap25","Slc17a7","Gad2",
                                          "Flt1", #Endo
                                          "Aspa", # Oligo
                                          "Gja1", #Astro
                                          "Neu4", #NF oligo
                                          "Pdgfra", #opc
                                          "C1qa"
                                          ),pt.size = 0.2)
```


```{r}
gene_List <- rownames(PFC_CCA_cocaine_Saline_sobj)
gene_List
gene_table <- data.frame(gene_List)
gene_table
write.csv(gene_table, "gene_table", row.names = FALSE)


```

```{r}

Idents(object = PFC_CCA_cocaine_Saline_sobj)
featureIEG <- c("Arc", "Egr2", "Fos", "Jun", "Junb", "Bdnf")

FeaturePlot(PFC_CCA_cocaine_Saline_sobj, featureIEG)

x1 <- c("pink", "blue")
x2 <- c("pink", "red")
panel<-data.frame(x1, x2)

p20 <- DotPlot(object=PFC_CCA_cocaine_Saline_sobj, features = featureIEG) + theme(axis.text.x = element_text(angle=90, size = 10.5,vjust=0.5,
     hjust = 0.5))
p20

p21 <- DotPlot(object = PFC_CCA_cocaine_Saline_sobj, features = featureIEG, split.by = "treatment", cols = panel) + theme(axis.text.x = element_text(angle=90, size = 10.5, vjust= 0.5, hjust = 0.5))
p21


```
## Plot some markers



#astro
```{r}
cell_type_list <- SplitObject(PFC_CCA_cocaine_Saline_sobj, split.by = "cell_type")
View(cell_type_list)

cell_type_Astro <- cell_type_list$`Astro`
Idents(cell_type_Astro) <- cell_type_Astro@meta.data$stage
Astro_Maintenance_withdraw_48h_withdraw_15d_de <- FindAllMarkers(cell_type_Astro)
head(Astro_Maintenance_withdraw_48h_withdraw_15d_de)
VlnPlot(object = cell_type_Astro, features = c("Mafb", "Npy", "Ly6c1", "Fli1", "Atp2b4", "Dqx1", log=T, pt.size = 0.2))


```
#exc
```{r}


cell_type_Excitatory <- cell_type_list$`Excitatory`
Idents(cell_type_Excitatory) <- cell_type_Excitatory@meta.data$stage
Excitatory_Maintenance_withdraw_48h_withdraw_15d_de <- FindAllMarkers(cell_type_Excitatory)
head(Excitatory_Maintenance_withdraw_48h_withdraw_15d_de)
VlnPlot(object = cell_type_Excitatory, features = c("Mafb", "Npy", "Ly6c1", "Fli1", "Atp2b4", "Dqx1", log=T, pt.size = 0.2))


```



#inhib
```{r}


cell_type_Inhibitory <- cell_type_list$`Inhibitory`
Idents(cell_type_Inhibitory) <- cell_type_Inhibitory@meta.data$stage
Inhibitory_Maintenance_withdraw_48h_withdraw_15d_de <- FindAllMarkers(cell_type_Inhibitory)
head(Inhibitory_Maintenance_withdraw_48h_withdraw_15d_de)
VlnPlot(object = cell_type_Inhibitory, features = c("Mafb", "Npy", "Ly6c1", "Fli1", "Atp2b4", "Dqx1", log=T, pt.size = 0.2))


```

#endo
```{r}


cell_type_Endo <- cell_type_list$`Endo`
Idents(cell_type_Endo) <- cell_type_Endo@meta.data$stage
Endo_Maintenance_withdraw_48h_withdraw_15d_de <- FindAllMarkers(cell_type_Endo)
head(Endo_Maintenance_withdraw_48h_withdraw_15d_de)
VlnPlot(object = cell_type_Endo, features = c("Mafb", "Npy", "Ly6c1", "Fli1", "Atp2b4", "Dqx1", log=T, pt.size = 0.2))


```
#Micro
```{r}


cell_type_Micro <- cell_type_list$`Micro`
Idents(cell_type_Micro) <- cell_type_Micro@meta.data$stage
Micro_Maintenance_withdraw_48h_withdraw_15d_de <- FindAllMarkers(cell_type_Micro)
head(Micro_Maintenance_withdraw_48h_withdraw_15d_de)
VlnPlot(object = cell_type_Micro, features = c("Mafb", "Npy", "Ly6c1", "Fli1", "Atp2b4", "Dqx1", log=T, pt.size = 0.2))


```
#oligo
```{r}


cell_type_Oligo <- cell_type_list$`Oligo`
Idents(cell_type_Oligo) <- cell_type_Oligo@meta.data$stage
Oligo_Maintenance_withdraw_48h_withdraw_15d_de <- FindAllMarkers(cell_type_Oligo)
head(Oligo_Maintenance_withdraw_48h_withdraw_15d_de)
VlnPlot(object = cell_type_Oligo, features = c("Mafb", "Npy", "Ly6c1", "Fli1", "Atp2b4", "Dqx1", log=T, pt.size = 0.2))


```
#OPC
```{r}


cell_type_OPC <- cell_type_list$`OPC`
Idents(cell_type_OPC) <- cell_type_OPC@meta.data$stage
OPC_Maintenance_withdraw_48h_withdraw_15d_de <- FindAllMarkers(cell_type_OPC)
head(OPC_Maintenance_withdraw_48h_withdraw_15d_de)
VlnPlot(object = cell_type_OPC, features = c("Mafb", "Npy", "Ly6c1", "Fli1", "Atp2b4", "Dqx1", log=T, pt.size = 0.2))


```

#Astro 2
```{r}
cell_type_list <- SplitObject(PFC_CCA_cocaine_Saline_sobj, split.by = "cell_type")
View(cell_type_list)

cell_type_Astro <- cell_type_list$`Astro`
Idents(cell_type_Astro) <- cell_type_Astro@meta.data$treatment
cell_type_Astro_cocaine<-subset(x = cell_type_Astro , idents = "Cocaine")

Idents(cell_type_Astro_cocaine) <- cell_type_Astro_cocaine@meta.data$stage

Astro_Maintenance_withdraw_48h_withdraw_15d_de <- FindAllMarkers(cell_type_Astro_cocaine)

View(Astro_Maintenance_withdraw_48h_withdraw_15d_de)
head(Astro_Maintenance_withdraw_48h_withdraw_15d_de)

VlnPlot(object = cell_type_Astro_cocaine, features = c("Fcer1g","Rpp25","Rph3a","Rrm2","Bcl11a
","Cdk14"),# log = T, pt.size = 0.2)
)
p9 <- DotPlot(object=cell_type_Astro_cocaine, features = c("Fcer1g","Rpp25","Rph3a","Rrm2","Bcl11a
","Cdk14")) +
    theme(axis.text = element_text(size = 8,
                                   angle = 90,
                                   hjust = 1))
p9

```
#Excitatory 2
```{r}


cell_type_Excitatory <- cell_type_list$`Excitatory`
Idents(cell_type_Excitatory) <- cell_type_Excitatory@meta.data$treatment
cell_type_Excitatory_cocaine<-subset(x = cell_type_Excitatory , idents = "Cocaine")

Idents(cell_type_Excitatory_cocaine) <- cell_type_Excitatory_cocaine@meta.data$stage

Excitatory_Maintenance_withdraw_48h_withdraw_15d_de <- FindAllMarkers(cell_type_Excitatory_cocaine)

View(Excitatory_Maintenance_withdraw_48h_withdraw_15d_de)
head(Excitatory_Maintenance_withdraw_48h_withdraw_15d_de)


VlnPlot(object = cell_type_Excitatory_cocaine, features = c("Lhx2","Nefl","Pdlim4","Pgcp","Slc15a2","Ctsz"),# log = T, pt.size = 0.2)
)
p10 <- DotPlot(object=cell_type_Excitatory_cocaine, features = c("Lhx2","Nefl","Pdlim4","Pgcp","Slc15a2","Ctsz")) +
    theme(axis.text = element_text(size = 8,
                                   angle = 90,
                                   hjust = 1))
p10

cell_type_Excitatory <- FindNeighbors(cell_type_Excitatory, reduction = "pca", dims = 1:50)
cell_type_Excitatory <- FindClusters(cell_type_Excitatory, resolution = 0.5)
Idents(object = PFC_CCA_cocaine_Saline_sobj) <- "cell_type"
featureIEG<-c("Arc", "Egr2", "Fos", "Fosb", "Jun", "Junb", "Bdnf")
#FeaturePlot(PFC_CCA_cocaine_Saline_sobj,featureIEG)
x1<-c("pink","blue")
x2<-c("pink","red")
panel<-data.frame(x1,x2)
p19 <- DotPlot(object=cell_type_Excitatory, features = featureIEG, split.by = "treatment", cols=panel) + theme(axis.text.x = element_text(angle=90, size = 10.5,vjust=0.5,
     hjust = 0.5))
p19

```

```{r}
cell_type_Excitatory <- cell_type_list$`Excitatory`
cell_type_Excitatory <- FindNeighbors(cell_type_Excitatory, reduction = "pca", dims = 1:50)
cell_type_Excitatory<- FindClusters(cell_type_Excitatory, resolution = 0.5)

p22 <- DimPlot(cell_type_Excitatory, 
               reduction = "umap", 
               group.by  = "seurat_clusters",
               label = T)
p22

p23 <- DotPlot(object = cell_type_Excitatory, features = featureIEG, split.by = "treatment", cols = panel) + theme(axis.text.x = element_text(angle=90, size = 10.5, vjust = 0.5, hjust = 0.5))
p23
```

```{r}
TSNEPlot(all_cell_inDD_sobj,do.label = T, group.by="CellType", colors.use = c("#9F248F", pal_simpsons()(10)[c(1,3:5,9:10)]),label.size = 5, do.return=TRUE,pt.size = 0.9)+
    ggtitle(paste0("PFC cells (n=",length(all_cell_inDD_sobj@cell.names)," cells)")) + 
    theme(plot.title = element_text(hjust = 0.5))


```

#Inhibitory 2
```{r}
cell_type_Inhibitory <- cell_type_list$`Inhibitory`
Idents(cell_type_Inhibitory) <- cell_type_Inhibitory@meta.data$treatment
cell_type_Inhibitory_cocaine<-subset(x = cell_type_Inhibitory , idents = "Cocaine")

Idents(cell_type_Inhibitory_cocaine) <- cell_type_Inhibitory_cocaine@meta.data$stage

Inhibitory_Maintenance_withdraw_48h_withdraw_15d_de <- FindAllMarkers(cell_type_Inhibitory_cocaine)

View(Inhibitory_Maintenance_withdraw_48h_withdraw_15d_de)
head(Inhibitory_Maintenance_withdraw_48h_withdraw_15d_de)


VlnPlot(object = cell_type_Inhibitory_cocaine, features = c("Inadl","Pon2","3110035E14Rik","Id1","Fgd5","A930038C07Rik"),# log = T, pt.size = 0.2)
)
p11 <- DotPlot(object=cell_type_Inhibitory_cocaine, features = c("Inadl","Pon2","3110035E14Rik","Id1","Fgd5","A930038C07Rik")) +
    theme(axis.text = element_text(size = 8,
                                   angle = 90,
                                   hjust = 1))
p11




```

#Endo 2
```{r}
cell_type_Endo <- cell_type_list$`Endo`
Idents(cell_type_Endo) <- cell_type_Endo@meta.data$treatment
cell_type_Endo_cocaine<-subset(x = cell_type_Endo , idents = "Cocaine")

Idents(cell_type_Endo_cocaine) <- cell_type_Endo_cocaine@meta.data$stage

Endo_Maintenance_withdraw_48h_withdraw_15d_de <- FindAllMarkers(cell_type_Endo_cocaine)

View(Endo_Maintenance_withdraw_48h_withdraw_15d_de)
head(Endo_Maintenance_withdraw_48h_withdraw_15d_de)

VlnPlot(object = cell_type_Endo_cocaine, features = c("Syn1","Mag","Wasf1","Meis2","Basp1", "Gng3"),# log = T, pt.size = 0.2)
)
p12 <- DotPlot(object=cell_type_Endo_cocaine, features = c("Syn1","Mag","Wasf1","Meis2","Basp1", "Gng3")) +
    theme(axis.text = element_text(size = 8,
                                   angle = 90,
                                   hjust = 1))
p12

```
#Micro 2
```{r}
cell_type_Micro <- cell_type_list$`Micro`
Idents(cell_type_Micro) <- cell_type_Micro@meta.data$treatment
cell_type_Micro_cocaine<-subset(x = cell_type_Micro , idents = "Cocaine")

Idents(cell_type_Micro_cocaine) <- cell_type_Micro_cocaine@meta.data$stage

Micro_Maintenance_withdraw_48h_withdraw_15d_de <- FindAllMarkers(cell_type_Micro_cocaine)

View(Micro_Maintenance_withdraw_48h_withdraw_15d_de)
head(Micro_Maintenance_withdraw_48h_withdraw_15d_de)

VlnPlot(object = cell_type_Micro_cocaine, features = c("Kcnh7","Necab1","Ifi204","Fam126b","Plscr1","Slc6a11"),# log = T, pt.size = 0.2)
)
p13 <- DotPlot(object=cell_type_Micro_cocaine, features = c("Kcnh7","Necab1","Ifi204","Fam126b","Plscr1","Slc6a11")) +
    theme(axis.text = element_text(size = 8,
                                   angle = 90,
                                   hjust = 1))
p13

```
#Oligo 2
```{r}
cell_type_Oligo <- cell_type_list$`Oligo`
Idents(cell_type_Oligo) <- cell_type_Oligo@meta.data$treatment
cell_type_Oligo_cocaine<-subset(x = cell_type_Oligo , idents = "Cocaine")

Idents(cell_type_Oligo_cocaine) <- cell_type_Oligo_cocaine@meta.data$stage

Oligo_Maintenance_withdraw_48h_withdraw_15d_de <- FindAllMarkers(cell_type_Oligo_cocaine)

View(Oligo_Maintenance_withdraw_48h_withdraw_15d_de)
head(Oligo_Maintenance_withdraw_48h_withdraw_15d_de)

VlnPlot(object = cell_type_Oligo_cocaine, features = c("Rbfox1","Tcn2","Ifngr1","Sulf2","Gap43","Itgb1"),# log = T, pt.size = 0.2)
)
p14 <- DotPlot(object=cell_type_Oligo_cocaine, features = c("Rbfox1","Tcn2","Ifngr1","Sulf2","Gap43","Itgb1")) +
    theme(axis.text = element_text(size = 8,
                                   angle = 90,
                                   hjust = 1))
p14

```

#OPC 2
```{r}
cell_type_OPC <- cell_type_list$`OPC`
Idents(cell_type_OPC) <- cell_type_OPC@meta.data$treatment
cell_type_OPC_cocaine<-subset(x = cell_type_OPC , idents = "Cocaine")

Idents(cell_type_OPC_cocaine) <- cell_type_OPC_cocaine@meta.data$stage

OPC_Maintenance_withdraw_48h_withdraw_15d_de <- FindAllMarkers(cell_type_OPC_cocaine)

View(OPC_Maintenance_withdraw_48h_withdraw_15d_de)
head(OPC_Maintenance_withdraw_48h_withdraw_15d_de)

VlnPlot(object = cell_type_OPC_cocaine, features = c("Mgat4c","Ubash3b","Cpne7","Lgals1","Prox1","Utrn"),# log = T, pt.size = 0.2)
)
p15 <- DotPlot(object=cell_type_OPC_cocaine, features = c("Mgat4c","Ubash3b","Cpne7","Lgals1","Prox1","Utrn")) +
    theme(axis.text = element_text(size = 8,
                                   angle = 90,
                                   hjust = 1))
p15

```
#NF Oligo 2
```{r}
cell_type_NF_Oligo <- cell_type_list$`NF Oligo`
Idents(cell_type_NF_Oligo) <- cell_type_NF_Oligo@meta.data$treatment
cell_type_NF_Oligo_cocaine<-subset(x = cell_type_NF_Oligo , idents = "Cocaine")

Idents(cell_type_NF_Oligo_cocaine) <- cell_type_NF_Oligo_cocaine@meta.data$stage

NF_Oligo_Maintenance_withdraw_48h_withdraw_15d_de <- FindAllMarkers(cell_type_NF_Oligo_cocaine)

View(NF_Oligo_Maintenance_withdraw_48h_withdraw_15d_de)
head(NF_Oligo_Maintenance_withdraw_48h_withdraw_15d_de)

VlnPlot(object = cell_type_NF_Oligo_cocaine, features = c("Lat", "Entpd2","Plekhh1","Rph3a","Expi","Odz2"),# log = T, pt.size = 0.2)
)
p16 <- DotPlot(object=cell_type_NF_Oligo_cocaine, features = c("Lat", "Entpd2","Plekhh1","Rph3a","Expi","Odz2")) +
    theme(axis.text = element_text(size = 8,
                                   angle = 90,
                                   hjust = 1))
p16

```

```{r}
TSNEPlot(all_cell_inDD_sobj,do.label = T, group.by="CellType", colors.use = c("#9F248F", pal_simpsons()(10)[c(1,3:5,9:10)]),label.size = 5, do.return=TRUE,pt.size = 0.9)+
    ggtitle(paste0("PFC cells (n=",length(all_cell_inDD_sobj@cell.names)," cells)")) + 
    theme(plot.title = element_text(hjust = 0.5))
```
```{r}

all_mrks <- FindAllMarkers(PFC_CCA_cocaine_Saline_sobj,logfc.threshold = 3,only.pos = T, test.use = "bimod")

CellType_markers =  FindMarkers(PFC_CCA_cocaine_Saline_sobj,ident.1 = "Excitatory", logfc.threshold = 1,
                  only.pos = T, test.use = "bimod")

tmp2$cluster <- "Excitatory"
tmp2$gene <- rownames(tmp2)

all_mrks <-  rbind(all_mrks,tmp2)


pdf("All_cell_markers.pdf",width = 15,height = 10 )
PlotMarketGenesHeatmap(PFC_CCA_cocaine_Saline_sobj,
                       CellType_markers,
                       pct.1.thr = 0.7,
                       pct.2.thr = 0.1,
                       is.pval = T)
dev.off()
                               
```

